GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-23 src/Output/decorations/latex/tpl.tex
Output

Following Varian’s advices, about ML and EC complementarities -i.e. merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The London School of Economics (LSE) “Testimation” approach -to obtain information about residual properties- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples. This methodology includes five complementary layers -handling cross-section, time series and panel data- see \cite{gsreg2019}: \begin{enumerate}
    \item Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions;

@@

\begin{lstlisting} 
      using GlobalSearchRegression
      GlobalSearchRegression.gsr(
        {{#input}}
        equation = "{{equation}}",
        data = {{data}},
        datanames = {{datanames}},
        method = :{{method}},
        intercept = {{intercept}},
        {{#panel}}panel = {{.}},{{/panel}}
        {{#time}}time = {{.}},{{/time}}
        {{#seasonaladjustment}}seasonaladjustment = {{.}},{{/seasonaladjustment}}
        removeoutliers = {{removeoutliers}},
        {{/input}}

        fe_sqr
        fe_log
        fe_inv
        fe_lag
        interaction
        preliminaryselection
        fixedvariables
        outsample
        criteria
        ttest
        modelavg
        residualtest
        orderresults
        kfoldcrossvalidation
        numfolds
        testsetshare
        exportcsv
        exportsummary
\end{lstlisting}

The report is structured as follows. After this introduction, the methodology is presented. In section 3, descriptive statistics are introduced. In turn, section 4 is dedicated to LASSO results. In turn, section 4 is dedicated to All-subset-regression results. After that, section 5 shows All-subset-regression results. Finally, the last section examines K-fold cross-validation outcomes.

@@

  {{#seasonalfortex}}
    \item Seasonal-adjustment: variables {{#:fe_seasonaladjustment_names}}{{.}}, {{/:fe_seasonaladjustment_names}}have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). For each one, the function removes the seasonal component using window lengths equal to {{#:fe_seasonaladjustment_vals}}{{.}}, {{/:fe_seasonaladjustment_vals}}respectively.
  {{/seasonalfortex}}

  {{#seasonalfortex2}}
  \item Seasonal-adjustment: variable {{#:fe_seasonaladjustment_names2}}{{.}}{{/:fe_seasonaladjustment_names2}} has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). The function removes the seasonal component using a window length equal to {{#:fe_seasonaladjustment_vals2}}{{.}}{{/:fe_seasonaladjustment_vals2}}.
  {{/seasonalfortex2}}

@@

In this Julia package, the best model among $2^{n}-1$ alternatives is selected using a potentially composite ordering variable defined as the equally-weighted average of normalized (to guarantee equal weights) and harmonized (to ensure that higher values always identify better models) user's specified criteria. For in-sample adjustment, available alternatives include: Adjusted R2 (:r2adj, the default), Bayesian information criteria (:bic), Akaike and Corrected Akaike information criteria (:aic and :aicc), Mallows's Cp statistic (:cp), Sum of squared errors (also known as Residual sum of squares, :sse) and the Root mean square error (:rmse). For out-of-sample accuracy, there is available the out-of-sample root mean square error (:rmsout). Users are free to combine in-sample and out-of-sample information criteria. In this report, selected information criteria include ({{#criteria_names}}{{.}}, {{/criteria_names}}the key variable/s for feature selection.

@@

\begin{enumerate}
  {{#intercept}}
  \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
  {{/intercept}}
  {{#outsample}}
  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to {{outsample}}.
  {{/outsample}}
  {{#ttest}}
  \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
  {{/ttest}}
  {{#modelavg}}
  \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option. More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
  {{/modelavg}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
  {{/residualtest}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
  {{/residualtest}}
  {{#orderresults}}  
  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
  {{/orderresults}}
\end{enumerate}
{{/allsubsetregression}}

--------------------------------------------------

{{#crossvalidation}}
\subsection{K-fold Cross Validation}

@@

\item For each sub-sample K, the time series methodology is reproduce henceforth.
\end{enumerate}
{{/panelid}}
{{/crossvalidation}}

{{#input}}
\section{Descriptive Statistics}

@@

\section{Variables}

@@

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
    \hline
              & \\
    Variables & {{ depvar }} \\
    \hline
    \hline
    {{#expvars}}
      {{ name }} & {{ coef }} \\
    {{/expvars}}
    \hline
    \hline
    Observations &  {{ nobs }} \\
    \lambda      &  {{ lambda }} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/preliminaryselection}}

{{#allsubsetregression}}
\section{Global Search Regression}

@@

    \begin{tabular}{l c{{#modelavg}} c{{/modelavg}}}
    \hline
    \hline
                 &  Best Model              {{#modelavg}} & Model Averaging           {{/modelavg}} \\
    Variables    &  {{depvar}}              {{#modelavg}} & {{depvar}}                {{/modelavg}} \\
    \hline{{#bmexpvars}} 
    {{name}}     & {{best.b}}{{best.stars}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
                 & {{best.bstd}}            {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
    {{/bmexpvars}}\hline

    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ } \\
    \hline
    \hline
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{Standard errors in parentheses} \\
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \end{tabular}
    {{/bestmodel}}
  \label{tab:addlabel}
\end{table}

@@

In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy. {{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria. On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
{{/allsubsetregression}}

@@

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}} \\
                 & {{kfolds}}-fold  & {{kfolds}}-fold \\
    Variables    & Mean             & Median          \\
    \hline
    \hline
                 &                  &                  \\
                 &                  &                  \\
    \hline

    Error out-sample &     &   \\
    Error in-sample  &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}

>>>>

Following Varian’s advices, about ML and EC complementarities -i.e. merging algorithms from different families to reduce both sampling and model uncertainty-, we are developing a novel multi-layer-multi-algorithm methodology combining two reinforcing paradigms: The London School of Economics (LSE) “Testimation” approach -to obtain information about residual properties- and the Bayesian-like “Double-model averaging” -across different covariates and sub-samples. This methodology includes five complementary layers -handling cross-section, time series and panel data- see \cite{gsreg2019}:

\begin{enumerate}
    \item Pre-processing: with outlier detection, missing values identification, seasonal adjustment and normalization/standardization functions;

@@

\begin{lstlisting} 
  using GlobalSearchRegression
  GlobalSearchRegression.gsr({{#input}}
    equation = "{{equation}}",
    data = {{data}},
    datanames = {{datanames}},
    method = :{{method}},
    intercept = {{intercept}},{{#panel}}
    panel = {{.}},{{/panel}}{{#time}}
    time = {{.}},{{/time}}{{#seasonaladjustment}}
    seasonaladjustment = {{.}},{{/seasonaladjustment}}
    removeoutliers = {{removeoutliers}},{{/input}}{{#featureextraction}}{{#fe_sqr}}
    fe_sqr = {{.}},{{/fe_sqr}}{{#fe_log}}
    fe_log = {{.}},{{/fe_log}}{{#fe_inv}}
    fe_inv = {{.}},{{/fe_inv}}{{#fe_lag}}
    fe_lag = {{.}},{{/fe_lag}}{{#interaction}}
    interaction = {{.}},{{/interaction}}{{/featureextraction}}{{#preliminaryselection}}
    preliminaryselection = :{{preliminaryselection}},{{/preliminaryselection}}{{#allsubsetregression}}{{#fixedvariables}}
    fixedvariables = {{.}},{{/fixedvariables}}{{#outsample}}
    outsample = {{.}},{{/outsample}}{{#criteria}}
    criteria = {{.}},{{/criteria}}
    ttest = {{ttest}},
    modelavg = {{modelavg}},
    residualtest = {{residualtest}},{{#orderresults}}
    orderresults = {{.}},{{/orderresults}}{{/allsubsetregression}}{{#crossvalidation}}
    kfoldcrossvalidation = {{.}},{{/crossvalidation}}{{#numfolds}}
    numfolds = {{.}},{{/numfolds}}{{#testsetshare}}
    testsetshare = {{.}}{{/testsetshare}}
  )
\end{lstlisting}

The report is structured as follows. After this introduction, the methodology is presented. In section 3, descriptive statistics are introduced. {{#preliminaryselection}}After that, LASSO results are examined.{{/preliminaryselection}} Then, All-subset-regression analysis is shown. {{#crossvalidation}}Finally, the last section examines K-fold cross-validation outcomes.{{/crossvalidation}}

@@

  {{#seasonaladjustment}}{{#seasonaladjustment}}
    {{#vars}}
      \item Seasonal-adjustment: variables {{#names}}{{.}}, {{/names}} have been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). For each one, the function removes the seasonal component using window lengths equal to {{#values}}{{.}}, {{/values}}respectively.
    {{/vars}}
    {{#var}}
      \item Seasonal-adjustment: variable {{#names}}{{.}}{{/names}}, has been selected for seasonal adjustment using \verb SingularSpectrumAnalysis.jl  (see \cite{hassani2007}). The function removes the seasonal component using a window length equal to {{#values}}{{.}}{{/values}}.
    {{/var}}
  {{/seasonaladjustment}}{{/seasonaladjustment}}

@@

In this Julia package, the best model among $2^{n}-1$ alternatives is selected using a potentially composite ordering variable defined as the equally-weighted average of normalized (to guarantee equal weights) and harmonized (to ensure that higher values always identify better models) user's specified criteria. For in-sample adjustment, available alternatives include: Adjusted R2 (:r2adj, the default), Bayesian information criteria (:bic), Akaike and Corrected Akaike information criteria (:aic and :aicc), Mallows's Cp statistic (:cp), Sum of squared errors (also known as Residual sum of squares, :sse) and the Root mean square error (:rmse). For out-of-sample accuracy, there is available the out-of-sample root mean square error (:rmsout). Users are free to combine in-sample and out-of-sample information criteria. In this report, selected information criteria include ({{criteria}}) as the key variable/s for feature selection.

@@

\begin{enumerate}
  {{#intercept}}
  \item Intercept has been included in all models. Alternatively, users could erase it by selecting the intercept=false boolean option.
  {{/intercept}}
  {{#outsample}}
  \item The outsample option identifies how many observations are used for prediction purposes. In this case, it has been set to {{outsample}}.
  {{/outsample}}
  {{#ttest}}
  \item The user's choice has been ttest=true. Therefore, standard deviation, ttest parameters and related probabilities has been calculated.
  {{/ttest}}
  {{#modelavg}}
  \item Across-models' average coefficients, t-tests and additional statistics were obtained using combined-criteria exponential weights because of the modelavg=true option. More precisely, each alternative model has a weight given by w1/sum(w1), where w1 is defined as exp(-delta/2) and delta is equal to max(index)-index -- where index is the above mentioned normalized, harmonized and potentially combined selection criteria--.
  {{/modelavg}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity and Jarque-Bera normality test to be implemented for each model.
  {{/residualtest}}
  {{#residualtest}}
  \item The residualtest=true option enables white heteroskedasticity, Jarque-Bera normality test and the Breusch-Godfrey test for autocorrelation to be implemented for each model.
  {{/residualtest}}
  {{#orderresults}}  
  \item User's specification of orderresults=true entails that the output matrix has been sorted by the the above mentioned normalized, harmonized and potentially combined selection criteria.
  {{/orderresults}}
\end{enumerate}
{{/allsubsetregression}}
{{#crossvalidation}}
\subsection{K-fold Cross Validation}

@@

\item For each sub-sample K, the time series methodology is reproduce henceforth.
\end{enumerate}
{{/panelid}}
{{/crossvalidation}}
{{#input}}
\section{Descriptive Statistics}

@@

@@

\begin{table}[!h]
  \centering
  \caption{LASSO Regression results}
    \begin{tabular}{l c}
    \hline
    \hline
              & \\
    Variables & {{ depvar }} \\
    \hline
    \hline
    {{#expvssars}}
      {{ name }} & {{ coef }} \\
    {{/expvssars}}
    \hline
    \hline
    Observations &  {{ nobs }} \\
    \lambda      &  {{ lassolambda }} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/preliminaryselection}}

{{#allsubsetregression}}

\clearpage
\section{Global Search Regression}

@@

    \begin{tabular}{l c{{#modelavg}} c{{/modelavg}}}
    \hline
    \hline
                 &  Best Model              {{#modelavg}} & Model Averaging           {{/modelavg}} \\
    Variables    &  {{depvar}}              {{#modelavg}} & {{depvar}}                {{/modelavg}} \\
    \hline{{#bmexpvars}} 
    {{name}}     & {{#best}}{{b}}{{stars}}{{/best}} {{#avg}} & {{b}}{{stars}}    {{/avg}} \\{{#ttest}}
                 & {{#best}}{{bstd}}{{/best}}       {{#avg}} & {{bstd}} {{/avg}} \\{{/ttest}}
    {{/bmexpvars}}\hline

    Observations &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ {{ nobs }} } \\
    Criteria     &   \multicolumn{ {{^avg}}1{{/avg}} {{#avg}}2{{/avg}} }{c}{ {{ criteria }} } \\
    \hline
    \hline
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{Standard errors in parentheses} \\
    \multicolumn{ {{^avg}}2{{/avg}} {{#avg}}3{{/avg}} }{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \end{tabular}
    {{/bestmodel}}
  \label{tab:addlabel}
\end{table}

@@

%In this figure it is shown that potential covariates included in the general unrrestricted model of the all-subset-regression algorithm display singnificant differences in terms of the user selected information criteria. For each explanatory variable information criteria gains were obtained as the differece between averages information criteria obtained from models which includes and excludes that covariate. Available statistics suggests that there {{are or is}} {{numofpositivegainsvariables}} explanatory {{variable or variables}} that improved model accuracy. {{Among them, {{bestvar}} or {{bestvar}}}} helps to increase up to a {{gainsinperc}}\% the user selected information criteria. On the contrary, there {{are or is}} {{numofnegativegainsvariables}} {{covariate or covariates}} that have a deleterious impact on model accuracy. This is specially true for {{worstvar}}, which seems to decrease up to a {{lossinperc}}\% the user selected information criteria}}
{{/allsubsetregression}}

@@

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
    Variables       & Mean                    & Median          \\
    \hline
    \hline
{{ median }}

--

{{ average }}

    {{#kfoldvars}}
      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
                    & {{ meanstd }}           & {{ medianstd }}           \\
    {{/kfoldvars}}
    \hline

    Error out-sample &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}
